### 2015-10-04 manuscript.Rnw
tweaks to makefile and MS for easier building

The function \texttt{tnrs\_match\_names} returns a data frame that lists the
Open Tree identifiers as well as other information to help users to ensure that
the taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. The argument \texttt{context\_name} can be used to limit potential
matches to a taxonomic group (see the function \texttt{tnrs_contexts} for a list
of possible options).  When this strategy cannot be used in case the tree
encompasses multiple domains (as in the present example), the function
\texttt{inspect} lists alternative matches for a taxon name, and \texttt{update}
replaces it in the results. An example of this approach is provided in the
vignette ``How to use rotl?'' that accompanies the package.

>>>>

The function \texttt{tnrs\_match\_names} returns a data frame that lists the
Open Tree identifiers as well as other information to help users to ensure that
the taxa matched are the correct ones. Here, there is no ambiguity in the taxa
matched, however, as the Open Tree Taxonomy includes taxa from bacteria, plants,
and animals that are regulated by different nomenclatural codes (ICNP, ICN and
ICZN respectively), OTL and \texttt{rotl} provide tools to deal with potential
hemihomonyms. The argument \texttt{context\_name} can be used to limit potential
matches to a taxonomic group (see the function \texttt{tnrs\_contexts} for a list
of possible options).  When this strategy cannot be used in case the tree
encompasses multiple domains (as in the present example), the function
\texttt{inspect} lists alternative matches for a taxon name, and \texttt{update}
replaces it in the results. An example of this approach is provided in the
vignette ``How to use rotl?'' that accompanies the package.
